Insert the article title here

### 2018-08-08 writeup/manuscript.tex
more intro

%%%%%%%%% Insert author address here
\address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
$^{2}$Department of Psychology, The Ohio State University, Columbus, USA\\
$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK
}

@@

A striking example of the effect of strategy is given by \cite{boot2006}. They asked participants to monitor a cluttered display for an object changing colour or object onset. Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance.

\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.

In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters. The Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016} was used to examine strategies in the use of feature-based attention. [See below and supplementary materials for a description of this paradigm.] Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to near optimal), and how often they changed search features. Further work has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.8$\cite{irons-leber2018}.

Using a different paradigm\cite{nowakowsak2017}, we aimed to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies in a simple visual search task involving arrays of line segments (see Figure \ref{fig:exampleStimuli}). The line segments were arranged such that those on one side of the display all had a very similar orientation, while those on the other side had higher variance. This was done so that if the target appeared on the homogeneous side, it would be highly salient. Trials in which the target appeared on the heterogeneous side of the display would be much harder. With these stimuli, the optimal eye movement strategy is to only search the heterogeneous half of the stimulus, as targets on the homogeneous side can be detected with peripheral vision. We found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher. Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.

@@

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.

@@

The study consists of three different paradigms from the visual search literature in which large individual differences were found \cite{nowakowsak2017, irons-leber2016, kristjansson2014}. Example stimuli can be seen in Figure \ref{fig:exampleStimuli}.

@@

In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}. \cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=.53$). However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.

@@

\subsubsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowsak2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with Pearson's $r \in [0.65-0.86]$ ($95\%$ confidence interval) for accuracy in finding targets on the hard heterogeneous half of the display. We get similar scores for the correlation between sessions \textit{a} and \textit{b} for heterogeneous targets, ($r \in [0.66-0.87]$), homogeneous targets ($r \in [0.56-0.82]$) and target absent ($r \in [0.65-0.86]$). The reduced correlation for the homogeneous targets is likely due to the restricted range.

@@

We can also look at the initial search strategies adopted by our participants \ref{fig:splithalf_summary}(c, d). Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.57, 0.83]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials). More importantly, as with \cite{nowakowsak2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.56, 0.84]$ and session b, $r \in [0.50, 0.81]$.

@@

The results presented above are somewhat surprising.

>>>>

%%%%%%%%% Insert author address here
\address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
$^{2}$Department of Psychology, The Ohio State University, Columbus, USA\\
$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK}

@@

A striking example of the effect of strategy is given by Boot and colleagues\cite{boot2006}. They asked participants to monitor a cluttered display for an object changing colour or object onset. Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance.

Proulx\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.

Eye movement strategies have also been shown to be an imporotant source or individual differences in visual search tasks. Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search pardigm (referred to here as the Split-Half Search Array paradigm) to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies involving arrays of line segments (see Figure \ref{fig:exampleStimuli}. The line segments were arranged such that those on one side of the display all had a very similar orientation, while those on the other side had higher variance. This was done so that if the target appeared on the homogeneous side, it would be highly salient. Trials in which the target appeared on the heterogeneous side of the display would be much harder. With these stimuli, the optimal eye movement strategy is to only search the heterogeneous half of the stimulus, as targets on the homogeneous side can be detected with peripheral vision. While some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher. Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.

A similar range of strategies, from random to near-optimal has been found by Irons \& Leber with the Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016}, designed to explore how feature-based attention is used. This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a 4th colour that varies from red, through purple, to blue and back again) with numerals written inside them (See Figure \ref{fig:exampleStimuli}). The target is a defined as a red or blue box with a numeral between 1 and 4, and on each trial a target of both type is present. The participant's task is to find one of either target as quickly as possible and report the numeral. One trials in which the 4th box colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters. As the 4th colour changes to through purple to blue, participants should udpate their strategy and search for the red target. The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to near optimal), and how often they changed search features. Further work has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r \approx 0.8$\cite{irons-leber2018}.

@@

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed `super-searchers' showed no switch cost.

There have been some efforts made to relate these differences to other measures such as measures of working memory or \ldots. \cite{Jóhannesson2017,}.  \ldots.

@@

The study consists of three different paradigms from the visual search literature in which large individual differences were found \cite{nowakowska2017, irons-leber2016, kristjansson2014}. Example stimuli can be seen in Figure \ref{fig:exampleStimuli}.

@@

In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}. \cite{nowakowska2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=.53$). However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.

@@

\subsubsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowska2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with Pearson's $r \in [0.65-0.86]$ ($95\%$ confidence interval) for accuracy in finding targets on the hard heterogeneous half of the display. We get similar scores for the correlation between sessions \textit{a} and \textit{b} for heterogeneous targets, ($r \in [0.66-0.87]$), homogeneous targets ($r \in [0.56-0.82]$) and target absent ($r \in [0.65-0.86]$). The reduced correlation for the homogeneous targets is likely due to the restricted range.

@@

We can also look at the initial search strategies adopted by our participants \ref{fig:splithalf_summary}(c, d). Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.57, 0.83]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials). More importantly, as with \cite{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.56, 0.84]$ and session b, $r \in [0.50, 0.81]$.

@@

The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms. While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of $r \in [0.65. 0.86]$ in the split-half paradigm and $r \in [0.72, 0.9]$ for the adaptive choice paradigm\cite{irons-leber2016}. [AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]
